An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/motiv.tex
minor motiv

\para{Example~4: Singular Value Errors} 
Many system performance problems are caused by 
issue that a value is set either too high or too low.
For example, a parameter relating to memory might be too large,
exhausting the RAM and causing extreme slowness or even a crash. 
Consider the following real-world misconfiguration file%
~\cite{singleValue}: a user was experiencing the ``My SQL Server 
has gone away" error.  
This is difficult to debug, since the error message is not specific.
It turns out the following line in her configuration file was problematic:

@@

The user eventually resolved the issue by replacing the above line with {\tt max\_allowed\_packet=2M}.
One possible way to reach this conclusion more quickly is to determine that the original value, 100 MB, 
was statistically deviant and extremely large for the {\tt max\_allowed\_packet} attribute. 
ConfigV can detect these
outliers. Run on the user's original configuration file, ConfigV would output:

>>>>

\para{Example~4: Singular Value Errors} 
Many system performance problems are caused by the
issue that a value is set either too high or too low.
For example, a parameter relating to memory might be too large,
exhausting the RAM and causing extreme slowness or even a crash. 
Consider the following real-world misconfiguration file%
~\cite{singleValue}: a user was experiencing the ``My SQL Server 
has gone away" error.  
This is difficult to debug, since the error message is not specific.
It turns out the following line in her configuration file was problematic:

@@

The user eventually resolved the issue by replacing the above line with {\tt max\_allowed\_packet=2M}.
One possible way to reach this conclusion more quickly is to determine that the original value, 100 MB, 
is statistically deviant and extremely large for the {\tt max\_allowed\_packet} attribute. 
ConfigV can detect these
outliers. Run on the user's original configuration file, ConfigV would output:
